A Theory for Data Migration of Generated Evolving Information Systems

### 2022-11-20 2022 Migration/articleMigration.tex
nabrander

\section{Analysis}
   Information systems are typically used by distributed actors (both users and computers) who continually work with data.
   A system $\infsys$ contains a dataset $\dataset$, which represents the state of the system.%
\footnote{Where ambiguity lures, we write $\dataset_{\infsys}$ instead of $\dataset$, to indicate that we specifically mean the dataset of $\infsys$.}
   Every event that an actor causes in system $\infsys$ may change the state $\dataset$ of that system.
   To keep our theory technology independent, we will assume that a dataset contains triples.
   Data migration occurs when an old system, $\infsys$, is replaced by a new system, $\infsys'$,
   while preserving the meaning of the data from $\infsys$ as much as possible.
   Just copying the set of data from $\infsys$ to $\infsys'$ is obviously wrong if the schemas of both systems differ.

   The schema $\schema$ of a system $\infsys$ is basically a set of semantic constraints on its dataset $\dataset$.%
\footnote{Where ambiguity lures, we write $\schema_{\infsys}$ instead of $\schema$ to indicate that we specifically mean the schema of $\infsys$.}
   The Ampersand compiler generates systems, which keep all constraints satisfied at all times.
   This is why we have done this research with Ampersand.
   Much like~\cite{Spivak2012}, in our work the schema encodes the semantics of a system.
   This will allow us to be explicit about ``preserving the meaning as much as possible''.
   In contrast with~\cite{Spivak2012}, our approach does not work with functions (functors)
   but with relations in a way that bears resemblance with Alloy~\cite{Alloy2006} and allegories%
\footnote{Allegories are a specific type of categories, which the reader does not need to understand for the purpose of this paper}~\cite{Zielinski2013}.

@@

   A schema $\schema$ is a triple $\triple{\concepts}{\rels}{\rules}$,
   in which $\concepts$ is a finite set of concepts,
   $\rels$ is a finite set of relations,
   and $\rules$ is a finite set of rules.
   Where ambiguity lures, we write $\concepts_{\schema}$, $rels_{\schema}$, and $\rules_{\schema}$ to indicate that we specifically mean the schema $\schema$.
%  Every schema is an element of an infinite set called $\Schema$.

>>>>

\section{Analysis}
   Information systems are typically used by distributed actors (both users and computers) who continually work with data.
   A system $\infsys$ contains a dataset $\dataset$, which represents the state of the system.
   We write $\dataset_{\infsys}$ to refer to dataset $\dataset$.
   Every event that an actor causes in system $\infsys$ may change the state $\dataset$ of that system.
   To keep our theory technology independent, we will assume that a dataset contains triples.
   Data migration occurs when an old system, $\infsys$, is replaced by a new system, $\infsys'$,
   while preserving the meaning of the data from $\infsys$ as much as possible.
   Just copying the set of data from $\infsys$ to $\infsys'$ is obviously wrong if the schemas of both systems differ.

   The schema $\schema$ of a system $\infsys$ is basically a set of semantic constraints on its dataset $\dataset$.
   We write $\schema_{\infsys}$ to refer to schema $\schema$.
   The Ampersand compiler generates systems, which keep all constraints satisfied at all times.
   This is why we have done this research with Ampersand.
   Much like~\cite{Spivak2012}, in our work the schema encodes the semantics of a system.
   This will allow us to be explicit about ``preserving the meaning as much as possible''.
   In contrast with~\cite{Spivak2012}, our approach does not work with functions (functors)
   but with relations in a way that bears resemblance with Alloy~\cite{Alloy2006} and allegories%
\footnote{Allegories are a specific type of categories, which the reader does not need to understand for the purpose of this paper}~\cite{Zielinski2013}.

@@

   A schema $\schema$ is a triple $\triple{\concepts}{\rels}{\rules}$,
   in which $\concepts$ is a finite set of concepts,
   $\rels$ is a finite set of relations,
   and $\rules$ is a finite set of rules.
   We write $\concepts_{\schema}$, $\rels_{\schema}$, and $\rules_{\schema}$ to refer to $\concepts$, $\rels$, and $\rules$ respectively.
%  Every schema is an element of an infinite set called $\Schema$.
